Imputation of Incomplete Multilevel Data with \pkg{mice}

### 2021-10-06 Multilevel Missing Data/Multilevel-Missing-Data.tex
Fill in basic info in Jstat template

\Abstract{
Tutorial paper on imputing incomplete multilevel data with \pkg{mice}.
Including methods for ignorable and non-ignorable missingness.
}

@@

\Address{
    Hanne Oberman\\
    Utrecht University\\
    First line\\
Second line\\
  E-mail: \email{name@company.com}\\
  URL: \url{http://rstudio.com}\\~\\
      }

@@

\hypertarget{introduction}{%
\section{Introduction}\label{introduction}}

This template demonstrates some of the basic LaTeX that you need to know
to create a JSS article.

\hypertarget{code-formatting}{%
\subsection{Code formatting}\label{code-formatting}}

In general, don't use Markdown, but use the more precise LaTeX commands
instead:

\begin{itemize}
\item
  \proglang{Java}
\item
  \pkg{plyr}
\end{itemize}

One exception is inline code, which can be written inside a pair of
backticks (i.e., using the Markdown syntax).

If you want to use LaTeX commands in headers, you need to provide a
\texttt{short-title} attribute. You can also provide a custom identifier
if necessary. See the header of Section \ref{r-code} for example.

\section[R code]{\proglang{R} code}\label{r-code}

Can be inserted in regular R markdown blocks.

\begin{CodeChunk}
\begin{CodeInput}
R> x <- 1:10
R> x
\end{CodeInput}
\begin{CodeOutput}
 [1]  1  2  3  4  5  6  7  8  9 10
\end{CodeOutput}
\end{CodeChunk}

\subsection[Features specific to rticles]{Features specific to
\pkg{rticles}}\label{features-specific-to}

\begin{itemize}
\tightlist
\item
  Adding short titles to section headers is a feature specific to
  \pkg{rticles} (implemented via a Pandoc Lua filter). This feature is
  currently not supported by Pandoc and we will update this template if
  \href{https://github.com/jgm/pandoc/issues/4409}{it is officially
  supported in the future}.
\item
  Using the \texttt{\textbackslash{}AND} syntax in the \texttt{author}
  field to add authors on a new line. This is a specific to the
  \texttt{rticles::jss\_article} format.
\end{itemize}

>>>>

\Abstract{
Tutorial paper on imputing incomplete multilevel data with \pkg{mice}.
Including methods for ignorable and non-ignorable missingness. AKA
missing on so many levels.
}

@@

\Address{
    Hanne Oberman\\
    Utrecht University\\
    First line\\
Second line\\
  E-mail: \email{h.i.oberman@uu.nl}\\
  URL: \url{https://hanneoberman.github.io/}\\~\\
      }

@@

\hypertarget{outline-door-thomas}{%
\section{Outline door Thomas}\label{outline-door-thomas}}

\begin{itemize}
\item
  Waarom zijn standaard (ad hoc) methoden niet geschikt?
\item
  Wat is heterogeniteit? (i.e.~variability binnen studies
  vs.~variability tussen studies). Random effects voor intercept term,
  predictor effects, en/of variance residual error
\item
  JOMO aanpak (misschien buiten beschouwing laten?)
\item
  MICE aanpak: one-stage imputation versus two-stage imputation methods
\item
  Imputatie van studie-level versus patient-level covariates
\item
  Omgaan met MNAR
\end{itemize}

\hypertarget{references}{%
\section{References}\label{references}}

\begin{itemize}
\item
  \href{Chapter:\%20Dealing\%20with\%20Missing\%20Data\%20in\%20an\%20IPD\%20Meta-analysis}{https://onlinelibrary.wiley.com/doi/abs/10.1002/9781119333784.ch18}
\item
  \href{Vignette:\%20gerkovink.com/miceVignettes/Multi_level}{https://www.gerkovink.com/miceVignettes/Multi\_level/Multi\_level\_data.html}
\end{itemize}
